---
title: "cfa_report"
author: "Thomas E. Metherell"
date: "2023-08-08"
format:
    html:
        code-fold: true
        toc: true
---

## Loading dependency and targets

```{r dependencies}
library(targets)
library(lavaan)
library(semTools)

swbs_country_cfa_model_MZexclude <- tar_read(swbs_country_cfa_model_MZexclude)
swbs_country_metric_model_MZexclude <- tar_read(swbs_country_metric_model_MZexclude)

anx_country_cfa_model <- tar_read(anx_country_cfa_model)
anx_country_metric_model <- tar_read(anx_country_metric_model)

cesd_country_cfa_model <- tar_read(cesd_country_cfa_model)
cesd_country_metric_model <- tar_read(cesd_country_metric_model)
```

## CW-SWBS
### Unconstrained CFA summary

```{r swbs_uc}
summary(swbs_country_cfa_model_MZexclude, fit.measures = TRUE, standardized = TRUE)
```

### Constrained CFA summary

```{r swbs_c}
summary(swbs_country_metric_model_MZexclude, fit.measures = TRUE, standardized = TRUE)
``` 

### Comparison between constrained and unconstrained models

```{r swbs_comp}
summary(compareFit(swbs_country_metric_model_MZexclude, swbs_country_cfa_model_MZexclude))
```

## Anxiety scale
### Unconstrained CFA summary

```{r anx_uc}
summary(anx_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### Constrained CFA summary

```{r anx_c}
summary(anx_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained and unconstrained models

```{r anx_comp}
summary(compareFit(anx_country_metric_model, anx_country_cfa_model))
```

## Abridged CES-D
### Unconstrained CFA summary

```{r cesd_uc}
summary(cesd_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### Constrained CFA summary

```{r cesd_c}
summary(cesd_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained and unconstrained models

```{r cesd_comp}
summary(compareFit(cesd_country_metric_model, cesd_country_cfa_model))
```