---
title: "cfa_report"
author: "Thomas E. Metherell"
date: "2023-08-08"
format:
    html:
        code-fold: true
        toc: true
---

## Loading dependencies and targets

```{r dependencies}
library(targets)
library(lavaan)
library(semTools)

swbs_country_cfa_model <- tar_read(swbs_country_cfa_model)
swbs_country_metric_model <- tar_read(swbs_country_metric_model)
swbs_country_scalar_model <- tar_read(swbs_country_scalar_model)

anx_country_cfa_model <- tar_read(anx_country_cfa_model)
anx_country_metric_model <- tar_read(anx_country_metric_model)
anx_country_scalar_model <- tar_read(anx_country_scalar_model)

cesd_country_cfa_model <- tar_read(cesd_country_cfa_model)
cesd_country_metric_model <- tar_read(cesd_country_metric_model)
cesd_country_scalar_model <- tar_read(cesd_country_scalar_model)

paykel_country_cfa_model <- tar_read(paykel_country_cfa_model)
paykel_country_metric_model <- tar_read(paykel_country_metric_model)
paykel_country_scalar_model <- tar_read(paykel_country_scalar_model)

anx_abridged_country_cfa_model <- tar_read(anx_abridged_country_cfa_model)
anx_abridged_country_metric_model <- tar_read(anx_abridged_country_metric_model)
anx_abridged_country_scalar_model <- tar_read(anx_abridged_country_scalar_model)

cesd_abridged_country_cfa_model <- tar_read(cesd_abridged_country_cfa_model)
cesd_abridged_country_metric_model <- tar_read(cesd_abridged_country_metric_model)
cesd_abridged_country_scalar_model <- tar_read(cesd_abridged_country_scalar_model)

paykel_abridged_country_cfa_model <- tar_read(paykel_abridged_country_cfa_model)
paykel_abridged_country_metric_model <- tar_read(paykel_abridged_country_metric_model)
paykel_abridged_country_scalar_model <- tar_read(paykel_abridged_country_scalar_model)
```

## CW-SWBS
### Unconstrained CFA summary

```{r swbs_uc}
summary(swbs_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r swbs_c}
summary(swbs_country_metric_model, fit.measures = TRUE, standardized = TRUE)
``` 

### CFA summary with loadings and intercepts constrained
```{r swbs_c2}
summary(swbs_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r swbs_comp}
summary(compareFit(swbs_country_metric_model, swbs_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r swbs_comp2}
summary(compareFit(swbs_country_scalar_model, swbs_country_metric_model))
```

## Anxiety scale
### Unconstrained CFA summary

```{r anx_uc}
summary(anx_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r anx_c}
summary(anx_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained

```{r anx_c2}
summary(anx_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r anx_comp}
summary(compareFit(anx_country_metric_model, anx_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r anx_comp2}
summary(compareFit(anx_country_scalar_model, anx_country_metric_model))
```

## CESD-R
### Unconstrained CFA summary

```{r cesd_uc}
summary(cesd_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r cesd_c}
summary(cesd_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained

```{r cesd_c2}
summary(cesd_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r cesd_comp}
tryCatch(summary(compareFit(cesd_country_metric_model, cesd_country_cfa_model)), error = function(e) cat("One or more models did not converge."))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r cesd_comp2}
tryCatch(summary(compareFit(cesd_country_scalar_model, cesd_country_metric_model)), error = function(e) cat("One or more models did not converge."))
```

## Paykel suicide scale
### Unconstrained CFA summary

```{r paykel_uc}
summary(paykel_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r paykel_c}
summary(paykel_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained
```{r paykel_c2}
summary(paykel_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r paykel_comp}
summary(compareFit(paykel_country_metric_model, paykel_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r paykel_comp2}
summary(compareFit(paykel_country_scalar_model, paykel_country_metric_model))
```

## Abridged anxiety scale
### Unconstrained CFA summary

```{r abridged_anx_uc}
summary(anx_abridged_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r abridged_anx_c}
summary(anx_abridged_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained
```{r abridged_anx_c2}
summary(anx_abridged_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r abridged_anx_comp}
summary(compareFit(anx_abridged_country_metric_model, anx_abridged_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r abridged_anx_comp2}
summary(compareFit(anx_abridged_country_scalar_model, anx_abridged_country_metric_model))
```

## Abridged CESD-R
### Unconstrained CFA summary

```{r abridged_cesd_uc}
summary(cesd_abridged_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r abridged_cesd_c}
summary(cesd_abridged_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained
```{r abridged_cesd_c2}
summary(cesd_abridged_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r abridged_cesd_comp}
summary(compareFit(cesd_abridged_country_metric_model, cesd_abridged_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r abridged_cesd_comp2}
summary(compareFit(cesd_abridged_country_scalar_model, cesd_abridged_country_metric_model))
```

## Abridged Paykel suicide scale
### Unconstrained CFA summary

```{r abridged_paykel_uc}
summary(paykel_abridged_country_cfa_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings constrained

```{r abridged_paykel_c}
summary(paykel_abridged_country_metric_model, fit.measures = TRUE, standardized = TRUE)
```

### CFA summary with loadings and intercepts constrained

```{r abridged_paykel_c2}
summary(paykel_abridged_country_scalar_model, fit.measures = TRUE, standardized = TRUE)
```

### Comparison between constrained loadings and unconstrained models

```{r abridged_paykel_comp}
summary(compareFit(paykel_abridged_country_metric_model, paykel_abridged_country_cfa_model))
```

### Comparison between constrained loadings and intercepts and constrained loadings models

```{r abridged_paykel_comp2}
summary(compareFit(paykel_abridged_country_scalar_model, paykel_abridged_country_metric_model))
```