---
title: "models_report"
author: "Thomas E. Metherell"
date: "2023-09-08"
format:
    html:
        code-fold: true
        toc: true
---

## Loading dependencies and targets

```{r dependencies}
library(targets)
library(bayesplot)

connection_ls_model <- tar_read(connection_ls_model)
connection_swbs_model <- tar_read(connection_swbs_model)
connection_anx_model <- tar_read(connection_anx_model)
connection_cesd_model <- tar_read(connection_cesd_model)
connection_sh_model <- tar_read(connection_sh_model)
connection_paykel_model <- tar_read(connection_paykel_model)

connection_ls_model_weighted <- tar_read(connection_ls_model_weighted)
connection_swbs_model_weighted <- tar_read(connection_swbs_model_weighted)
connection_anx_model_weighted <- tar_read(connection_anx_model_weighted)
connection_cesd_model_weighted <- tar_read(connection_cesd_model_weighted)
connection_sh_model_weighted <- tar_read(connection_sh_model_weighted)
connection_paykel_model_weighted <- tar_read(connection_paykel_model_weighted)

internet_ls_model <- tar_read(internet_ls_model)
internet_swbs_model <- tar_read(internet_swbs_model)
internet_anx_model <- tar_read(internet_anx_model)
internet_cesd_model <- tar_read(internet_cesd_model)
internet_sh_model <- tar_read(internet_sh_model)
internet_paykel_model <- tar_read(internet_paykel_model)

internet_ls_model_weighted <- tar_read(internet_ls_model_weighted)
internet_swbs_model_weighted <- tar_read(internet_swbs_model_weighted)
internet_anx_model_weighted <- tar_read(internet_anx_model_weighted)
internet_cesd_model_weighted <- tar_read(internet_cesd_model_weighted)
internet_sh_model_weighted <- tar_read(internet_sh_model_weighted)
internet_paykel_model_weighted <- tar_read(internet_paykel_model_weighted)
```

## Models for ability to stay connected during lockdown
### Life satisfaction
#### Unweighted

```{r conn_ls}
plot(connection_ls_model)
summary(connection_ls_model)
```

#### Weighted

```{r conn_ls_weighted}
plot(connection_ls_model_weighted)
summary(connection_ls_model_weighted)
```

### CW-SWBS
#### Unweighted

```{r conn_swbs}
plot(connection_swbs_model)
summary(connection_swbs_model)
```

#### Weighted

```{r conn_swbs_weighted}
plot(connection_swbs_model_weighted)
summary(connection_swbs_model_weighted)
```

### Anxiety
#### Unweighted

```{r conn_anx}
plot(connection_anx_model)
summary(connection_anx_model)
```

#### Weighted

```{r conn_anx_weighted}
plot(connection_anx_model_weighted)
summary(connection_anx_model_weighted)
```

### CES-D
#### Unweighted

```{r conn_cesd}
plot(connection_cesd_model)
summary(connection_cesd_model)
```

#### Weighted

```{r conn_cesd_weighted}
plot(connection_cesd_model_weighted)
summary(connection_cesd_model_weighted)
```

### Self-harm
#### Unweighted

```{r conn_sh}
plot(connection_sh_model)
summary(connection_sh_model)
```

#### Weighted

```{r conn_sh_weighted}
plot(connection_sh_model_weighted)
summary(connection_sh_model_weighted)
```

### Paykel suicide scale
#### Unweighted

```{r conn_paykel}
plot(connection_paykel_model)
summary(connection_paykel_model)
```

#### Weighted

```{r conn_paykel_weighted}
plot(connection_paykel_model_weighted)
summary(connection_paykel_model_weighted)
```

## Models for internet use frequency
### Life satisfaction
#### Unweighted

```{r int_ls}
plot(internet_ls_model)
summary(internet_ls_model)
```

#### Weighted

```{r int_ls_weighted}
plot(internet_ls_model_weighted)
summary(internet_ls_model_weighted)
```

### CW-SWBS
#### Unweighted

```{r int_swbs}
plot(internet_swbs_model)
summary(internet_swbs_model)
```

#### Weighted

```{r int_swbs_weighted}
plot(internet_swbs_model_weighted)
summary(internet_swbs_model_weighted)
```

### Anxiety
#### Unweighted

```{r int_anx}
plot(internet_anx_model)
summary(internet_anx_model)
```

#### Weighted

```{r int_anx_weighted}
plot(internet_anx_model_weighted)
summary(internet_anx_model_weighted)
```

### CES-D
#### Unweighted

```{r int_cesd}
plot(internet_cesd_model)
summary(internet_cesd_model)
```

#### Weighted

```{r int_cesd_weighted}
plot(internet_cesd_model_weighted)
summary(internet_cesd_model_weighted)
```

### Self-harm
#### Unweighted

```{r int_sh}
plot(internet_sh_model)
summary(internet_sh_model)
```

#### Weighted

```{r int_sh_weighted}
plot(internet_sh_model_weighted)
summary(internet_sh_model_weighted)
```

### Paykel suicide scale
#### Unweighted

```{r int_paykel}
plot(internet_paykel_model)
summary(internet_paykel_model)
```

#### Weighted

```{r int_paykel_weighted}
plot(internet_paykel_model_weighted)
summary(internet_paykel_model_weighted)
```