---
title: "sensitivity_report"
author: "Thomas E. Metherell"
date: "2024-02-23"
format:
    html:
        code-fold: true
        toc: true
        toc-depth: 5
execute:
    output: asis
---

## Loading dependencies and targets

```{r dependencies}
library(targets)
library(dplyr)
library(ggplot2)
library(knitr)
library(mice)
library(mitools)

pooled_connection_ls_models_fullwb_summary <- tar_read(pooled_connection_ls_models_fullwb_summary)
pooled_connection_swbs_models_fullwb_summary <- tar_read(pooled_connection_swbs_models_fullwb_summary)
pooled_connection_anx_models_fullwb_summary <- tar_read(pooled_connection_anx_models_fullwb_summary)
pooled_connection_cesd_models_fullwb_summary <- tar_read(pooled_connection_cesd_models_fullwb_summary)
pooled_connection_sh_models_fullwb_summary <- tar_read(pooled_connection_sh_models_fullwb_summary)
pooled_connection_paykel_models_fullwb_summary <- tar_read(pooled_connection_paykel_models_fullwb_summary)

pooled_connection_ls_models_fullwb_weighted_summary <- tar_read(pooled_connection_ls_models_fullwb_weighted_summary)
pooled_connection_swbs_models_fullwb_weighted_summary <- tar_read(pooled_connection_swbs_models_fullwb_weighted_summary)
pooled_connection_anx_models_fullwb_weighted_summary <- tar_read(pooled_connection_anx_models_fullwb_weighted_summary)
pooled_connection_cesd_models_fullwb_weighted_summary <- tar_read(pooled_connection_cesd_models_fullwb_weighted_summary)
pooled_connection_sh_models_fullwb_weighted_summary <- tar_read(pooled_connection_sh_models_fullwb_weighted_summary)
pooled_connection_paykel_models_fullwb_weighted_summary <- tar_read(pooled_connection_paykel_models_fullwb_weighted_summary)

pooled_connection_ls_models_fullwb_relevelled_summary <- tar_read(pooled_connection_ls_models_fullwb_relevelled_summary)
pooled_connection_swbs_models_fullwb_relevelled_summary <- tar_read(pooled_connection_swbs_models_fullwb_relevelled_summary)
pooled_connection_anx_models_fullwb_relevelled_summary <- tar_read(pooled_connection_anx_models_fullwb_relevelled_summary)
pooled_connection_cesd_models_fullwb_relevelled_summary <- tar_read(pooled_connection_cesd_models_fullwb_relevelled_summary)
pooled_connection_sh_models_fullwb_relevelled_summary <- tar_read(pooled_connection_sh_models_fullwb_relevelled_summary)
pooled_connection_paykel_models_fullwb_relevelled_summary <- tar_read(pooled_connection_paykel_models_fullwb_relevelled_summary)

pooled_connection_ls_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_ls_models_fullwb_relevelled_weighted_summary)
pooled_connection_swbs_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_swbs_models_fullwb_relevelled_weighted_summary)
pooled_connection_anx_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_anx_models_fullwb_relevelled_weighted_summary)
pooled_connection_cesd_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_cesd_models_fullwb_relevelled_weighted_summary)
pooled_connection_sh_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_sh_models_fullwb_relevelled_weighted_summary)
pooled_connection_paykel_models_fullwb_relevelled_weighted_summary <- tar_read(pooled_connection_paykel_models_fullwb_relevelled_weighted_summary)

pooled_internet_ls_models_fullwb_summary <- tar_read(pooled_internet_ls_models_fullwb_summary)
pooled_internet_swbs_models_fullwb_summary <- tar_read(pooled_internet_swbs_models_fullwb_summary)
pooled_internet_anx_models_fullwb_summary <- tar_read(pooled_internet_anx_models_fullwb_summary)
pooled_internet_cesd_models_fullwb_summary <- tar_read(pooled_internet_cesd_models_fullwb_summary)
pooled_internet_sh_models_fullwb_summary <- tar_read(pooled_internet_sh_models_fullwb_summary)
pooled_internet_paykel_models_fullwb_summary <- tar_read(pooled_internet_paykel_models_fullwb_summary)

pooled_internet_ls_models_fullwb_weighted_summary <- tar_read(pooled_internet_ls_models_fullwb_weighted_summary)
pooled_internet_swbs_models_fullwb_weighted_summary <- tar_read(pooled_internet_swbs_models_fullwb_weighted_summary)
pooled_internet_anx_models_fullwb_weighted_summary <- tar_read(pooled_internet_anx_models_fullwb_weighted_summary)
pooled_internet_cesd_models_fullwb_weighted_summary <- tar_read(pooled_internet_cesd_models_fullwb_weighted_summary)
pooled_internet_sh_models_fullwb_weighted_summary <- tar_read(pooled_internet_sh_models_fullwb_weighted_summary)
pooled_internet_paykel_models_fullwb_weighted_summary <- tar_read(pooled_internet_paykel_models_fullwb_weighted_summary)

connection_ls_models_fullwb_summary <- tar_read(connection_ls_models_fullwb_summary)
connection_swbs_models_fullwb_summary <- tar_read(connection_swbs_models_fullwb_summary)
connection_anx_models_fullwb_summary <- tar_read(connection_anx_models_fullwb_summary)
connection_cesd_models_fullwb_summary <- tar_read(connection_cesd_models_fullwb_summary)
connection_sh_models_fullwb_summary <- tar_read(connection_sh_models_fullwb_summary)
connection_paykel_models_fullwb_summary <- tar_read(connection_paykel_models_fullwb_summary)

connection_ls_models_fullwb_weighted_summary <- tar_read(connection_ls_models_fullwb_weighted_summary)
connection_swbs_models_fullwb_weighted_summary <- tar_read(connection_swbs_models_fullwb_weighted_summary)
connection_anx_models_fullwb_weighted_summary <- tar_read(connection_anx_models_fullwb_weighted_summary)
connection_cesd_models_fullwb_weighted_summary <- tar_read(connection_cesd_models_fullwb_weighted_summary)
connection_sh_models_fullwb_weighted_summary <- tar_read(connection_sh_models_fullwb_weighted_summary)
connection_paykel_models_fullwb_weighted_summary <- tar_read(connection_paykel_models_fullwb_weighted_summary)

connection_ls_models_fullwb_relevelled_summary <- tar_read(connection_ls_models_fullwb_relevelled_summary)
connection_swbs_models_fullwb_relevelled_summary <- tar_read(connection_swbs_models_fullwb_relevelled_summary)
connection_anx_models_fullwb_relevelled_summary <- tar_read(connection_anx_models_fullwb_relevelled_summary)
connection_cesd_models_fullwb_relevelled_summary <- tar_read(connection_cesd_models_fullwb_relevelled_summary)
connection_sh_models_fullwb_relevelled_summary <- tar_read(connection_sh_models_fullwb_relevelled_summary)
connection_paykel_models_fullwb_relevelled_summary <- tar_read(connection_paykel_models_fullwb_relevelled_summary)

connection_ls_models_fullwb_relevelled_weighted_summary <- tar_read(connection_ls_models_fullwb_relevelled_weighted_summary)
connection_swbs_models_fullwb_relevelled_weighted_summary <- tar_read(connection_swbs_models_fullwb_relevelled_weighted_summary)
connection_anx_models_fullwb_relevelled_weighted_summary <- tar_read(connection_anx_models_fullwb_relevelled_weighted_summary)
connection_cesd_models_fullwb_relevelled_weighted_summary <- tar_read(connection_cesd_models_fullwb_relevelled_weighted_summary)
connection_sh_models_fullwb_relevelled_weighted_summary <- tar_read(connection_sh_models_fullwb_relevelled_weighted_summary)
connection_paykel_models_fullwb_relevelled_weighted_summary <- tar_read(connection_paykel_models_fullwb_relevelled_weighted_summary)

internet_ls_models_fullwb_summary <- tar_read(internet_ls_models_fullwb_summary)
internet_swbs_models_fullwb_summary <- tar_read(internet_swbs_models_fullwb_summary)
internet_anx_models_fullwb_summary <- tar_read(internet_anx_models_fullwb_summary)
internet_cesd_models_fullwb_summary <- tar_read(internet_cesd_models_fullwb_summary)
internet_sh_models_fullwb_summary <- tar_read(internet_sh_models_fullwb_summary)
internet_paykel_models_fullwb_summary <- tar_read(internet_paykel_models_fullwb_summary)

internet_ls_models_fullwb_weighted_summary <- tar_read(internet_ls_models_fullwb_weighted_summary)
internet_swbs_models_fullwb_weighted_summary <- tar_read(internet_swbs_models_fullwb_weighted_summary)
internet_anx_models_fullwb_weighted_summary <- tar_read(internet_anx_models_fullwb_weighted_summary)
internet_cesd_models_fullwb_weighted_summary <- tar_read(internet_cesd_models_fullwb_weighted_summary)
internet_sh_models_fullwb_weighted_summary <- tar_read(internet_sh_models_fullwb_weighted_summary)
internet_paykel_models_fullwb_weighted_summary <- tar_read(internet_paykel_models_fullwb_weighted_summary)
```

## Defining plotting functions

```{r plot_fn}
connection_plot <- function(summary){
    ggplot(
        summary %>% 
            mutate(term = case_when(
                term == "dv_covid_statusLockdown, connected" ~ "Yes",
                term == "dv_covid_statusLockdown, disconnected" ~ "No",
                term == "dv_covid_statusNo lockdown" ~ "No lockdown"
            )),
            aes(
            x = country, 
            y = estimate, 
            fill = term, 
            ymin = estimate + qt(0.025, df) * std.error,
            ymax = estimate + qt(0.975, df) * std.error
            )   
    ) +
    geom_col(position = "dodge") + 
    geom_errorbar(position = position_dodge(width = 0.9), width = 0.5) + 
    labs(x = "Country", y = "Coefficient", fill = "Connected with\nfriends and family\nduring lockdown?") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

internet_plots <- function(summary){
    country_list <- c("Ethiopia", "Kenya", "Mozambique", "Namibia", "Uganda", "Cambodia", "Indonesia", "Malaysia", "Philippines", "Thailand", "Vietnam")

    plots <- list()
    
    for(i in seq_along(country_list)){
        country <- country_list[i]

        temp <- summary[summary$country == country,]

        B1coef <- temp$estimate[temp$term == "B1"]
        B1se <- temp$std.error[temp$term == "B1"]
        B1df <- temp$df[temp$term == "B1"]
        B1lower <- B1coef + qt(0.025, B1df) * B1se
        B1upper <- B1coef + qt(0.975, B1df) * B1se
        CO2coef <- temp$estimate[temp$term == "CO21"]
        CO2se <- temp$std.error[temp$term == "CO21"]
        CO2lower <- CO2coef + qt(0.025, B1df) * CO2se
        CO2upper <- CO2coef + qt(0.975, B1df) * CO2se
        interactioncoef <- temp$estimate[temp$term == "B1:CO21"]
        interactionse <- temp$std.error[temp$term == "B1:CO21"]
        interactionlower <- interactioncoef + qt(0.025, B1df) * interactionse
        interactionupper <- interactioncoef + qt(0.975, B1df) * interactionse

        plot_data <- data.frame(
            B1 = rep(0:5 / 5, 2),
            CO2 = c(rep(0, 6), rep(1, 6))
        )

        plot_data$estimate <- B1coef * plot_data$B1 + CO2coef * plot_data$CO2 + interactioncoef * plot_data$B1 * plot_data$CO2

        plot_data$upper <- B1upper * plot_data$B1 + CO2upper * plot_data$CO2 + interactionupper * plot_data$B1 * plot_data$CO2

        plot_data$lower <- B1lower * plot_data$B1 + CO2lower * plot_data$CO2 + interactionlower * plot_data$B1 * plot_data$CO2

        plot_data$B1 <- as.factor(plot_data$B1)
        plot_data$CO2 <- as.factor(plot_data$CO2)

        plots[[i]] <- ggplot(
            plot_data,
            aes(
                x = B1,
                y = estimate,
                ymin = lower,
                ymax = upper,
                fill = CO2
            )
        ) +
        facet_wrap(vars(CO2), labeller = labeller(CO2 = c("0" = "No lockdown", "1" = "Lockdown"))) +
        geom_col() +
        geom_errorbar(width = 1/12) +
        scale_x_discrete(labels = c("Rarely", "At least every month", "At least every week", "At least every day", "Several times each day", "Almost all the time")) +
        labs(x = "Frequency of internet use", y = "Coefficient", title = country) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")
    }

    return(plots)
}
```

## Defining results printing function

```{r print_fn}
round_summary <- function(summary){
    for(i in 1:ncol(summary)){
        if(is.numeric(summary[, i])){
            summary[, i] <- round(summary[, i], 3)
        }
    }

    return(summary)
}

summary_list <- c("All participants", "Boys", "Girls", "Rural", "Urban", "Rural boys", "Urban boys", "Rural girls", "Urban girls")

print_summary <- function(summary){
    for(i in seq_along(summary_list)){
        cat(paste("#####", summary_list[i], "\n"))
        print(summary[[i]] |> round_summary() |> kable())
    }
}
```

## Models for ability to stay connected during lockdown ("no lockdown" as reference group)
### Life satisfaction
#### Pooled, unweighted

```{r pooled_conn_ls}
print_summary(pooled_connection_ls_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_ls_weighted}
print_summary(pooled_connection_ls_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_ls}
print_summary(connection_ls_models_fullwb_summary)
```

#### By country, weighted

```{r conn_ls_weighted}
print_summary(connection_ls_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_ls_plot}
connection_plot(connection_ls_models_fullwb_weighted_summary[[1]])
```

### CW-SWBS
#### Pooled, unweighted

```{r pooled_conn_swbs}
print_summary(pooled_connection_swbs_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_swbs_weighted}
print_summary(pooled_connection_swbs_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_swbs}
print_summary(connection_swbs_models_fullwb_summary)
```

#### By country, weighted

```{r conn_swbs_weighted}
print_summary(connection_swbs_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_swbs_weighted_plot}
connection_plot(connection_swbs_models_fullwb_weighted_summary[[1]])
```

### Anxiety
#### Pooled, unweighted

```{r pooled_conn_anx}
print_summary(pooled_connection_anx_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_anx_weighted}
print_summary(pooled_connection_anx_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_anx}
print_summary(connection_anx_models_fullwb_summary)
```

#### By country, weighted

```{r conn_anx_weighted}
print_summary(connection_anx_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_anx_weighted_plot}
connection_plot(connection_anx_models_fullwb_weighted_summary[[1]])
```

### CES-D
#### Pooled, unweighted

```{r pooled_conn_cesd}
print_summary(pooled_connection_cesd_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_cesd_weighted}
print_summary(pooled_connection_cesd_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_cesd}
print_summary(connection_cesd_models_fullwb_summary)
```

#### By country, weighted

```{r conn_cesd_weighted}
print_summary(connection_cesd_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_cesd_weighted_plot}
connection_plot(connection_cesd_models_fullwb_weighted_summary[[1]])
```

### Self-harm
#### Pooled, unweighted

```{r pooled_conn_sh}
print_summary(pooled_connection_sh_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_sh_weighted}
print_summary(pooled_connection_sh_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_sh}
print_summary(connection_sh_models_fullwb_summary)
```

#### By country, weighted

```{r conn_sh_weighted}
print_summary(connection_sh_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_sh_weighted_plot}
connection_plot(connection_sh_models_fullwb_weighted_summary[[1]])
```

### Paykel suicide scale
#### Pooled, unweighted

```{r pooled_conn_paykel}
print_summary(pooled_connection_paykel_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_conn_paykel_weighted}
print_summary(pooled_connection_paykel_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r conn_paykel}
print_summary(connection_paykel_models_fullwb_summary)
```

#### By country, weighted

```{r conn_paykel_weighted}
print_summary(connection_paykel_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r conn_paykel_weighted_plot}
connection_plot(connection_paykel_models_fullwb_weighted_summary[[1]])
```

## Models for ability to stay connected during lockdown ("lockdown, disconnected" as reference group)
### Life satisfaction
#### Pooled, unweighted

```{r pooled_conn_ls_relevelled}
print_summary(pooled_connection_ls_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_ls_relevelled_weighted}
print_summary(pooled_connection_ls_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_ls_relevelled}
print_summary(connection_ls_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_ls_relevelled_weighted}
print_summary(connection_ls_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_ls_relevelled_weighted_plot}
connection_plot(connection_ls_models_fullwb_relevelled_weighted_summary[[1]])
```

### CW-SWBS
#### Pooled, unweighted

```{r pooled_conn_swbs_relevelled}
print_summary(pooled_connection_swbs_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_swbs_relevelled_weighted}
print_summary(pooled_connection_swbs_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_swbs_relevelled}
print_summary(connection_swbs_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_swbs_relevelled_weighted}
print_summary(connection_swbs_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_swbs_relevelled_weighted_plot}
connection_plot(connection_swbs_models_fullwb_relevelled_weighted_summary[[1]])
```

### Anxiety
#### Pooled, unweighted

```{r pooled_conn_anx_relevelled}
print_summary(pooled_connection_anx_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_anx_relevelled_weighted}
print_summary(pooled_connection_anx_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_anx_relevelled}
print_summary(connection_anx_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_anx_relevelled_weighted}
print_summary(connection_anx_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_anx_relevelled_weighted_plot}
connection_plot(connection_anx_models_fullwb_relevelled_weighted_summary[[1]])
```

### CES-D
#### Pooled, unweighted

```{r pooled_conn_cesd_relevelled}
print_summary(pooled_connection_cesd_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_cesd_relevelled_weighted}
print_summary(pooled_connection_cesd_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_cesd_relevelled}
print_summary(connection_cesd_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_cesd_relevelled_weighted}
print_summary(connection_cesd_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_cesd_relevelled_weighted_plot}
connection_plot(connection_cesd_models_fullwb_relevelled_weighted_summary[[1]])
```

### Self-harm
#### Pooled, unweighted

```{r pooled_conn_sh_relevelled}
print_summary(pooled_connection_sh_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_sh_relevelled_weighted}
print_summary(pooled_connection_sh_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_sh_relevelled}
print_summary(connection_sh_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_sh_relevelled_weighted}
print_summary(connection_sh_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_sh_relevelled_weighted_plot}
connection_plot(connection_sh_models_fullwb_relevelled_weighted_summary[[1]])
```

### Paykel suicide scale
#### Pooled, unweighted

```{r pooled_conn_paykel_relevelled}
print_summary(pooled_connection_paykel_models_fullwb_relevelled_summary)
```

#### Pooled, weighted

```{r pooled_conn_paykel_relevelled_weighted}
print_summary(pooled_connection_paykel_models_fullwb_relevelled_weighted_summary)
```

#### By country, unweighted

```{r conn_paykel_relevelled}
print_summary(connection_paykel_models_fullwb_relevelled_summary)
```

#### By country, weighted

```{r conn_paykel_relevelled_weighted}
print_summary(connection_paykel_models_fullwb_relevelled_weighted_summary)
```

##### Plot (all participants)

```{r conn_paykel_relevelled_weighted_plot}
connection_plot(connection_paykel_models_fullwb_relevelled_weighted_summary[[1]])
```

## Models for internet use frequency
### Life satisfaction
#### Pooled, unweighted

```{r pooled_int_ls}
print_summary(pooled_internet_ls_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_ls_weighted}
print_summary(pooled_internet_ls_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_ls}
print_summary(internet_ls_models_fullwb_summary)
```

#### By country, weighted

```{r int_ls_weighted}
print_summary(internet_ls_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_ls_weighted_plots}
internet_plots(internet_ls_models_fullwb_weighted_summary[[1]])
```

### CW-SWBS
#### Pooled, unweighted

```{r pooled_int_swbs}
print_summary(pooled_internet_swbs_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_swbs_weighted}
print_summary(pooled_internet_swbs_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_swbs}
print_summary(internet_swbs_models_fullwb_summary)
```

#### By country, weighted

```{r int_swbs_weighted}
print_summary(internet_swbs_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_swbs_weighted_plots}
internet_plots(internet_swbs_models_fullwb_weighted_summary[[1]])
```

### Anxiety
#### Pooled, unweighted

```{r pooled_int_anx}
print_summary(pooled_internet_anx_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_anx_weighted}
print_summary(pooled_internet_anx_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_anx}
print_summary(internet_anx_models_fullwb_summary)
```

#### By country, weighted

```{r int_anx_weighted}
print_summary(internet_anx_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_anx_weighted_plots}
internet_plots(internet_anx_models_fullwb_weighted_summary[[1]])
```

### CES-D
#### Pooled, unweighted

```{r pooled_int_cesd}
print_summary(pooled_internet_cesd_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_cesd_weighted}
print_summary(pooled_internet_cesd_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_cesd}
print_summary(internet_cesd_models_fullwb_summary)
```

#### By country, weighted

```{r int_cesd_weighted}
print_summary(internet_cesd_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_cesd_weighted_plots}
internet_plots(internet_cesd_models_fullwb_weighted_summary[[1]])
```

### Self-harm
#### Pooled, unweighted

```{r pooled_int_sh}
print_summary(pooled_internet_sh_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_sh_weighted}
print_summary(pooled_internet_sh_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_sh}
print_summary(internet_sh_models_fullwb_summary)
```

#### By country, weighted

```{r int_sh_weighted}
print_summary(internet_sh_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_sh_weighted_plots}
internet_plots(internet_sh_models_fullwb_weighted_summary[[1]])
```

### Paykel suicide scale
#### Pooled, unweighted

```{r pooled_int_paykel}
print_summary(pooled_internet_paykel_models_fullwb_summary)
```

#### Pooled, weighted

```{r pooled_int_paykel_weighted}
print_summary(pooled_internet_paykel_models_fullwb_weighted_summary)
```

#### By country, unweighted

```{r int_paykel}
print_summary(internet_paykel_models_fullwb_summary)
```

#### By country, weighted

```{r int_paykel_weighted}
print_summary(internet_paykel_models_fullwb_weighted_summary)
```

##### Plot (all participants)

```{r int_paykel_weighted_plots}
internet_plots(internet_paykel_models_fullwb_weighted_summary[[1]])
```